Brownian dynamics simulation of cytoplasmic dynein's powerstroke reproduces bidirectional stepping

### 2021-06-02 papers/paper/paper.tex
add comments to paper

@@

\begin{figure}[tbhp]
\centering
\includegraphics[width=\linewidth]{figures/model-cartoon-simple.pdf}
\caption{\textbf{Basic geometric model in pre-stroke and post-stroke states.} \textit{Left: } Pre-stroke model of dynein with one MTBD bound to microtubule and the other free. Angles are measured from the $+\hat{x}$ direction. \textit{Right: } Post-stroke model with both MTBDs bound to microtubule. MTBD angles are relative to $+\hat{x}$ direction, and motor angles are between stalk and tail. Lengths and radii not to scale.}
\label{fig:model}
\end{figure}

\begin{figure}[tbhp]
\includegraphics[width=0.4\linewidth]{../../plots/burgess-model-figure.pdf}%
\includegraphics[width=0.6\linewidth]{../../plots/grotjahn-model-figure.pdf}%
%% \includegraphics[width=0.3\linewidth]{../../plots/crystal-model-figure.pdf}%
\caption{\textbf{Scale model compared with experimental images.} \textit{Left:} Model with angles at pre-stroke equilibrium superimposed over axonemal dynein c heavy chain micrograph in the pre-stroke ADP-Vi-bound state \cite{burgess-paper}. Interdomain lengths and radii scaled to micrograph scale bar. No microtubule is present, so $\theta_{nb}$ is arbitrary. \textit{Right: } Model with angles at pre-stroke equilibrium superimposed over density map of full-length native cytoplasmic dynein with accessory tail proteins (map ID EMD-7000) \cite{grotjahn}. Interdomain lengths and radii scaled to density map.}
\label{fig:micrographs}
\end{figure}

@@

\begin{table}
  \centering
  \begin{tabular}{lrrr}
    Param & Model & Experimental & Source \\
    \hline
%    $c_b$ & $\cb \Delta G_{ATP}$ &  & \\
    $c_m$ & $\cm \Delta G_{ATP}$ &  & \\
    $c_t$ & $\ct \Delta G_{ATP}$ &  & \\
    $k_a$ & $\kstk$  $s^{-1}$ &  & \\
    $k_b$ & $\kb$  nm $s^{-1}$ &  & \\
    $\epsilon$ &  $\MTbindingdistance$ nm & & \\
    $k_{ub}$ & $\kub$ $s^{-1}$ & & \\
    $C$ & $\cexp$ & & \\
    $L_s$ & $\ls$ nm & $21$ nm & \cite{Burgess2003, 3vkh-cite, carter-paper}\\
    $L_t$ & $\lt$ nm & $23$ nm & \cite{Burgess2003, 3vkh-cite, carter-paper}\\
%    $\theta_b$ & $\eqb$ &  120 & \cite{leschziner} \\
    $\theta_m^{\mbox{pre}}$ & $\eqmpre$ &  197 & \cite{Burgess2003}\\
    $\theta_m^{\mbox{post}}$ & $\eqmpost$ & 242 & \cite{Burgess2003}\\
    $\theta_t$ & $\eqt$ &  & \\
    $R_t$ & $\radiust$ nm & $4$ nm & \cite{Burgess2003}\\
    $R_m$ & $\radiusm$ nm & $5.5$ nm & \cite{Burgess2003}\\
    $R_b$ & $\radiusb$ nm & $1.25$ nm & \cite{Burgess2003}\\
    \hline
  \end{tabular}
  \caption{Parameters used in simulation. $c_b$, $c_m$ and $c_t$ are the MTBD, motor and tail spring constants, respectively. $k_b$ and $k_{ub}$ are the rates of pre-stroke to post-stroke and post-stroke to pre-stroke transitions, respectively. $L_s$ and $L_t$ are the lengths of the stalk and tail interdomain linkers. $c$ is the tension-gating factor. The $\theta$ values are the equilibrium values for each angle, where $\theta_m^{\mbox{pre}}$ is the equilibrium angle for the unbound motor in pre-stroke, whereas $\theta_m^{\mbox{post}}$ is the equilibrium angle for the bound pre-stroke motor and both post-stroke motors. $R_b$, $R_m$ and $R_t$ are the MTBD, motor and tail radii. Parameters used for all simulations unless otherwise noted}
  \label{table:params}
\end{table}

@@

\subsection*{Equilibrium forces}
The prestroke state has four degrees of freedom: $\theta_{bb}, \theta_{bm}, \theta_{um}$ and $\theta_{ub}$. The poststroke state has two: $\theta_{nm}$ and $\theta_{fm}$. The model is free to vary across all of these degrees of freedom, depending on its state, barring steric interactions with the microtubule. These angles describe a planar model which is not capable of transverse motion. To capture the gross dynamics and interdomain oscillations of the protein, restoring forces are imposed on each angle about equilibrium angles $\theta^{eq}_{bb}, \theta^{eq}_{bm}, \theta^{eq}_{um}, \theta^{eq}_{ub}$ for prestroke and $\theta^{eq}_{nm}$ and $\theta^{eq}_{fm}$ for poststroke. Each domain $i$ has a harmonic energy $c_i\left(\theta_i-\theta^{eq}_i\right)^2$ which exerts a restoring force pushing it back to equilibrium, where $c_b$, $c_m$ and $c_t$ are spring constants for each domain. These equilibrium angles are taken to be the average angle occupied by the protein in solution, and are thus extracted from EM micrographs, shown in Figure \ref{fig:micrographs}. These angles were extracted from axonemal dynein, but structural similarity suggests they should be applicable to cytoplasmic dynein as well \cite{dynein-c-paper}. Electron microscopy studies using ADP-Vi to freeze dynein in the pre-stroke state allow for both pre- and post-stroke equilibrium angles to be found \cite{burgess-paper}.

@@

>>>>

\davidsays{Main point: earlier models cannot explain the experimentally observed correlation between
  the initial displacement and step size.

  Introduce experiment first, esp. Yildiz.

  Explain existing models a bit more.  Not many details about each model, but for every model explain what
  it does and does not explain.

  QUESTION: Do we want to give the geometric argument for a typical final displacement?

  QUESTION: What predictions can we make?

  There should be many very short-distance steps that are not shown in experiment.

  The typical time spent actually taking a step (i.e. one-bound) should be very short.  (Be quantitative.)
  It's not been measured, and puts a limit on the time spent getting ready to rebind.  Does this mean we
  want the onebound time histogram?  I think not, but we do want the average value, and maybe median or similar?

  Power stroke model works? Even if the stalk does not do work by exerting torque.  Does that make
  it a winch model? This will require discussion early and late.

  Future work: add a backwards force to the model.
}

@@

\begin{figure}[tbhp]
\centering
\includegraphics[width=\linewidth]{figures/model-cartoon-simple.pdf}
\caption{\textbf{Basic geometric model in pre-stroke and post-stroke states.}
\davidsays{FIXME remove spring on binding domain and fix caption.}
\textit{Left: } Pre-stroke model of dynein with one MTBD bound to microtubule
and the other free. Angles are measured from the $+\hat{x}$ direction.
\textit{Right: } Post-stroke model with both MTBDs bound to microtubule. MTBD
angles are relative to $+\hat{x}$ direction, and motor angles are between stalk
and tail. Lengths and radii not to scale.}
\label{fig:model}
\end{figure}

\begin{figure}[tbhp]
  \centering
\includegraphics[width=0.5\linewidth]{../../plots/burgess-model-figure.pdf}%
% \includegraphics[width=0.6\linewidth]{../../plots/grotjahn-model-figure.pdf}%
%% \includegraphics[width=0.3\linewidth]{../../plots/crystal-model-figure.pdf}%
\caption{\textbf{Scale model compared with experimental images.}
%  \textit{Left:}
 Model with angles at pre-stroke equilibrium superimposed over
 axonemal dynein c heavy chain micrograph in the pre-stroke ADP-Vi-bound state
 \cite{burgess-paper}. Interdomain lengths and radii scaled to micrograph scale
 bar. % No microtubule is present, so $\theta_{nb}$ is arbitrary.
%   \textit{Right: }
%  Model with angles at pre-stroke equilibrium superimposed over density map of
%  full-length native cytoplasmic dynein with accessory tail proteins (map ID
%  EMD-7000) \cite{grotjahn}. Interdomain lengths and radii scaled to density
%  map.
 }
\label{fig:micrographs}
\end{figure}

@@

\begin{table}
  \centering
  \begin{tabular}{lrrr}
    Param & Model & Experimental & Source \\
    \hline
%    $c_b$ & $\cb \Delta G_{ATP}$ &  & \\
    $c_m$ & $\cm \Delta G_{ATP}$ &  & \\
    $c_t$ & $\ct \Delta G_{ATP}$ &  & \\
    $k_a$ & $\kstk$  $s^{-1}$ &  & \\
    $k_b$ & $\kb$  nm $s^{-1}$ &  & \\
    $\epsilon$ &  $\MTbindingdistance$ nm & & \\
    $k_{ub}$ & $\kub$ $s^{-1}$ & & \\
    $C$ & $\cexp$ & & \\
    $L_s$ & $\ls$ nm & $21$ nm & \cite{Burgess2003, 3vkh-cite, carter-paper}\\
    $L_t$ & $\lt$ nm & $23$ nm & \cite{Burgess2003, 3vkh-cite, carter-paper}\\
%    $\theta_b$ & $\eqb$ &  120 & \cite{leschziner} \\
    $\theta_m^{\mbox{pre}}$ & $\eqmpre^\circ$ &  197$^\circ$ & \cite{Burgess2003}\\
    $\theta_m^{\mbox{post}}$ & $\eqmpost^\circ$ & 242$^\circ$ & \cite{Burgess2003}\\
    $\theta_t$ & $\eqt^\circ$ &  & \\
    $R_t$ & $\radiust$ nm & $4$ nm & \cite{Burgess2003}\\
    $R_m$ & $\radiusm$ nm & $5.5$ nm & \cite{Burgess2003}\\
    $R_b$ & $\radiusb$ nm & $1.25$ nm & \cite{Burgess2003}\\
    \hline
  \end{tabular}
  \caption{Parameters used in simulation. $c_b$, $c_m$ and $c_t$ are the MTBD, motor and tail spring constants, respectively. $k_b$ and $k_{ub}$ are the rates of pre-stroke to post-stroke and post-stroke to pre-stroke transitions, respectively. $L_s$ and $L_t$ are the lengths of the stalk and tail interdomain linkers. $c$ is the tension-gating factor. The $\theta$ values are the equilibrium values for each angle, where $\theta_m^{\mbox{pre}}$ is the equilibrium angle for the unbound motor in pre-stroke, whereas $\theta_m^{\mbox{post}}$ is the equilibrium angle for the bound pre-stroke motor and both post-stroke motors. $R_b$, $R_m$ and $R_t$ are the MTBD, motor and tail radii. Parameters used for all simulations unless otherwise noted}
  \label{table:params}
\end{table}

@@

\davidsays{Maybe we want to discuss right here the likely step sizes for leading and trailing steps
\emph{if it goes to its equilibrium configuration}.  It's pretty simple and can serve as a ``validation"
of our model geometry.}

\subsection*{Equilibrium forces}
The prestroke state has four degrees of freedom: $\theta_{bb}, \theta_{bm},
\theta_{um}$ and $\theta_{ub}$. The poststroke state has two: $\theta_{nm}$ and
$\theta_{fm}$. The model is free to vary across all of these degrees of freedom,
depending on its state, barring steric interactions with the microtubule. These
angles describe a planar model which is not capable of transverse motion.  \davidsays{FIXME edit here.} To
capture the gross dynamics and interdomain oscillations of the protein,
restoring forces are imposed on each angle about equilibrium angles
$\theta^{eq}_{bb}, \theta^{eq}_{bm}, \theta^{eq}_{um}, \theta^{eq}_{ub}$ for
prestroke and $\theta^{eq}_{nm}$ and $\theta^{eq}_{fm}$ for poststroke. Each
domain $i$ has a harmonic energy $c_i\left(\theta_i-\theta^{eq}_i\right)^2$
which exerts a restoring force pushing it back to equilibrium, where $c_b$,
$c_m$ and $c_t$ are spring constants for each domain. These equilibrium angles
are taken to be the average angle occupied by the protein in solution, and are
thus extracted from EM micrographs, shown in Figure \ref{fig:micrographs}. These
angles were extracted from axonemal dynein, but structural similarity suggests
they should be applicable to cytoplasmic dynein as well \cite{dynein-c-paper}.
Electron microscopy studies using ADP-Vi to freeze dynein in the pre-stroke
state allow for both pre- and post-stroke equilibrium angles to be found
\cite{burgess-paper}.

@@

\davidsays{Discuss each figure, and each parameter (how we got it).}

\davidsays{Fig. \ref{fig:ProbLagPlot} gives us the exponential unbinding constant. Also rerun to get better.

Explain that the bothbound time does not vary by more than X\% regardless of initial $L$ in our model.
}

\davidsays{Do not add average both-bound time vs. L? This is a measurable prediction if we can't find an experimental
result.  Otherwise, we can compare with experiment.  Maybe just add a sentence or two}

\davidsays{histogram plot.  It shows that we are stepping the right distance, our springs are not too stiff,
    and our angles work out.  Report the average step length.}

\davidsays{contour plot. Gave us the binding rate and the affinity time.  
Very fast binding required (to get slope right) and need affinity time to avoid instantly
 rebinding.}

 \davidsays{Trajectory plot.  Similar to experiment. The bothbound time determines velocity and depends on ATP.}

 \davidsays{one-bound time plot. Cut?}
